Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2020-07-14 area_agg_seq_tsas.tex
added data and codes availability statement

@@

The data and codes used in this case study 
can be found at \emph{figshare} 
(see \url{https://figshare.com/s/199e049e2a0f9c18d19a}).
The data was derived from open-access dataset TOP10NL,
which is a topographic map produced by Kadaster
(see \url{https://www.pdok.nl/downloads/-/article/basisregistratie-topografie-brt-topnl}).

>>>>

\setcopyright{othergov}
\acmYear{2020} \acmVolume{1} \acmNumber{1} \acmArticle{1} \acmMonth{1} \acmPrice{15.00}\acmDOI{10.1145/3409290}

@@

The data and codes used in this case study 
can be found at \emph{figshare} 
(see \url{https://doi.org/10.1145/3409290} or
\url{https://figshare.com/articles/software/Data_and_codes_for_optimal_sequences/12652853}).
This data set has been substantially preprocessed and 
does not represent the land use as recorded by the German mapping authorities.
For ATKIS test data that has not been preprocessed, please refer to
\url{https://www.lgln.niedersachsen.de/startseite/online_angebote_amp_services/service/testdaten/testdaten-51644.html}.
